National Longitudinal Evidence for Growth in Subjective Wellbeing from Spiritual Beliefs

### 2020-11-19 Analysis.Rmd
committing figures

# Inference holds but VIFS for years x beliefs

```{r model centering years, include = FALSE}
library(lme4)
mod.1a <-lmer (PWI ~  1 +  yearsC * Beliefs +  Age.10yrs.C + Deprivation.S + Edu.S  + Employed + EthnicCats + Male  + Partner  + Pol.Orient.S + Urban + (1|Id), data= dfben, na.action = na.omit)
mod.2a <-lmer (LIFESAT ~ 1 + yearsC * Beliefs+ Age.10yrs.C + Deprivation.S + Edu.S  + Employed + EthnicCats + Male  + Partner  + Pol.Orient.S + Urban + (1|Id), data= dfben, na.action = na.omit)
summary(mod.1)
summary(mod.2)
# identical result
performance::check_collinearity(mod.1a)
performance::check_collinearity(mod.2a)

@@

>>>>

Inference holds but VIFS years x beliefs when years are centered.

```{r model centering years}
library(lme4)
mod.1a <-lmer (PWI ~  1 +  yearsC * Beliefs +  Age.10yrs.C + Deprivation.S + Edu.S  + Employed + EthnicCats + Male  + Partner  + Pol.Orient.S + Urban + (1|Id), data= dfben, na.action = na.omit)
mod.2a <-lmer (LIFESAT ~ 1 + yearsC * Beliefs+ Age.10yrs.C + Deprivation.S + Edu.S  + Employed + EthnicCats + Male  + Partner  + Pol.Orient.S + Urban + (1|Id), data= dfben, na.action = na.omit)
summary(mod.1a)
summary(mod.2a)
# identical result
performance::check_collinearity(mod.1a)
performance::check_collinearity(mod.2a)

@@

Model is robust without covariates

```{r robust to years and beliefs only}
library(lme4)
mod.1aa <-lmer (PWI ~  1 +  years * Beliefs + (1|Id), data= dfben, na.action = na.omit)
mod.2aa <-lmer (LIFESAT ~ 1 + years * Beliefs + (1|Id), data= dfben, na.action = na.omit)
)
# identical result
sjPlot::tab_model(mod.1aa,mod.2aa)
```
